Upper Limits on CN from Falling Evaporating Bodies\\seen towards \bp{}

### 2024-07-18 src/tex/ms.tex
[showyourwork] overleaf sync

This removes the blaze function, but there remain low spatial frequency variations between different nights, due to the changing slit illumination as the star moves across the spit aperture.

@@

After the initial data analysis, we proceed to with our search for lines from \ce{CN}.
%
Although we are interested in lines from the exocomets, we first coadd the data from all the individual epochs, in the stellar rest-frame, to obtain a deep search for circumstellar \ce{CN} absorption.
%
These coadded spectra for \ac{harps} and \ac{uves} are shown in \hl{Figure}.
%
No obvious feature jumps out, and we can rule out circumstellar \ce{CN} down to \hl{NNNN}.

Since the exocomets have a clear radial velocity with respect to \bp{}, and since each exocomet will have its own distinct velocity, we selected the NN epochs with the strongest exocometary features, a seen in the \ion{Ca}{ii} H \& K lines, as well as the MM epochs with the weakest cometary features.
%
The selection was done by

The spectra with only weak exocometary features were co-averaged in the stellar restframe in order to create a stellar master spectrum. This master-spectrum was divided out of all the remaining spectra in order to create relative spectra. 
The relative velocities of the exocomets were determined by ......., and the spectra were shifted to the rest-frames of these comments, before being combined. The combined exocomet aligned spectra for both the CA H\&K lines and \ce{CN} band are shown in Fig.~\ref{fig:coadd_exocomets}. As can be seen no signal is visibly present. [Do we need to add a correction to account for any radiation pressure, if so, is there a way to estimate that?]

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/two_CN_temps.pdf}
        \caption{Theoretical cross section spectra of CN for 100K and 1000K.}
        \label{fig:CN_theory}
        \script{plot_two_CN_temps.py}
    \end{centering}
\end{figure}

@@

      The authors thank the Lorentz Centre at Leiden University for organising the workshop ``Exocomets: Understanding the Composition of Planetary Building Blocks'' which led to the study in this paper. 
%
      Part of this work was supported by the German
      \emph{Deut\-sche For\-schungs\-ge\-mein\-schaft, DFG\/} project
      number Ts~17/2--1.
      %
We made use of the {\tt Python} programming language \citep{rossum1995} and the open-source {\tt Python} packages {\tt numpy} \citep{walt2011}, {\tt matplotlib} \citep{hunter2007}, {\tt astropy} \citep{astropy2013}.
%      
An online repository with materials used in this work is available at \url{https://github.com/sebastian-zieba/betaPic_comet}
\end{acknowledgements}

>>>>

This removes the blaze function, but there remain low spatial frequency variations between different nights, due to the changing slit illumination as the star moves across the slit aperture.

@@

After the initial data analysis, we proceed to with our search for lines from \ce{CN}.
%
Although we are interested in lines from the exocomets, we first co-add the data from all the individual epochs, in the stellar rest-frame, to obtain a deep search for circumstellar \ce{CN} absorption.
%
These coadded spectra for \ac{harps} and \ac{uves} are shown in \hl{Figure}.
%
No obvious feature jumps out, and we can rule out circumstellar \ce{CN} down to \hl{NNNN}.

Since the exocomets have a clear radial velocity with respect to \bp{}, and since each exocomet will have its own distinct velocity, we selected the NN epochs with the strongest exocometary features, a seen in the \ion{Ca}{ii} H \& K lines, as well as the MM epochs with the weakest cometary features.
%
The spectra with only weak exocometary features were co-averaged in the stellar rest frame in order to create a stellar master spectrum. This master-spectrum was divided out of all the remaining spectra in order to create relative spectra. 
%
The relative velocities of the exocomets were determined by ......., and the spectra were shifted to the rest-frames of these comments, before being combined.
%
The combined exocomet aligned spectra for both the \ce{Ca} H\&K lines and \ce{CN} band are shown in Fig.~\ref{fig:coadd_exocomets}. As can be seen no signal is visibly present.
%
[Do we need to add a correction to account for any radiation pressure, if so, is there a way to estimate that?]

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/two_CN_temps.pdf}
        \caption{Model spectrum for CN.}
        \label{fig:CN_theory}
        \script{plot_two_CN_temps.py}
    \end{centering}
\end{figure}

@@

The authors thank the Lorentz Centre at Leiden University for organising the workshop ``Exocomets: Understanding the Composition of Planetary Building Blocks'' which led to the study in this paper. 
%
Part of this work was supported by the German \emph{Deut\-sche For\-schungs\-ge\-mein\-schaft, DFG\/} project number Ts~17/2--1.
%
We made use of the {\tt Python} programming language \citep{rossum1995} and the open-source {\tt Python} packages {\tt numpy} \citep{walt2011}, {\tt matplotlib} \citep{hunter2007}, {\tt astropy} \citep{astropy2013}.
%      
An online repository with materials used in this work is available at \url{https://github.com/mkenworthy/}
\end{acknowledgements}
